### 2017-09-30 TF-vldb2018/sec-intro.tex

\stab (1) We propose {\em team simulation}, a revision of traditional graph pattern matching, for top-$k$ team formation (Section~\ref{sec-tsim}).
It extends existing methods by incorporating the structural and capacity constraints using pattern graphs.
To cope with the highly dynamic environment of team formation, we also formulate the dynamic top-$k$ team formation problem  (Section~\ref{sec-tsim}), for handling separate and simultaneous pattern and data updates.

\stab (2) We develop a batch algorithm for computing top-$k$ teams via team simulation (Section~\ref{sec-tsimAlg}).
We study the satisfiability problem for pattern graphs, a new problem raised in the presence of capacity bounds for graph pattern matching.
We also propose two optimization techniques, incrementally computing radius varied balls and density based filtering, for speeding up computations.

>>>>

\stab (1) We propose {\em team simulation}, a revision of traditional graph pattern matching, for top-$k$ team formation (Section~\ref{sec-tsim}).
It extends existing methods by incorporating the structural and capacity constraints using pattern graphs.
To cope with the highly dynamic environment of team formation, we also formulate the dynamic top-$k$ team formation problem  (Section~\ref{sec-tsim}), for dealing with pattern and data updates, separately and simultaneously.

\stab (2) We develop a batch algorithm for computing top-$k$ teams via team simulation (Section~\ref{sec-tsimAlg}).
We study the satisfiability problem for pattern graphs, a new problem raised in the presence of capacity bounds for graph pattern matching.
We also propose two optimization techniques, handling radius varied balls and density based filtering, for speeding up the process of computations.
